A Mountaintop View Requires Minimal Sorting: \break An Instance Optimal Contour Tree Algorithm

### 2014-10-30 paint-contour-tree.tex
fig 2 changed

\begin{figure}[h]\centering
    \includegraphics[width=.3\linewidth,height=.42\linewidth]{figs/shaded}%
    \hspace{.5in}
    \includegraphics[width=.3\linewidth,height=.42\linewidth]{figs/trees2}
    \caption{On the left, a surface will a balanced contour tree, but whose join and split trees have long tails.  
    On the right (in clockwise order from the top) the contour, split and join trees.}
    \label{fig:sorting}
\end{figure}

>>>>

% \begin{figure}[h]\centering
%     \includegraphics[width=.3\linewidth,height=.42\linewidth]{figs/shaded}%
%     \hspace{.5in}
%     \includegraphics[width=.3\linewidth,height=.42\linewidth]{figs/trees2}
%     \caption{On the left, a surface will a balanced contour tree, but whose join and split trees have long tails.  
%     On the right (in clockwise order from the top) the contour, split and join trees.}
%     \label{fig:sorting}
% \end{figure}
\begin{figure}[h]\centering
    \includegraphics[width=.7\linewidth,height=.28\linewidth]{figs/balanced2}
    \includegraphics[width=.7\linewidth,height=.25\linewidth]{figs/trees}
    \caption{On top, a surface will a balanced contour tree, but whose join and split trees have long tails.  
    On bottom (from left to right), the contour, join and split trees.}
    \label{fig:sorting}
\end{figure}
